Replication of \"Anti-Immigrant Rhetoric and ICE Reporting Interest: Evidence

### 2024-06-28 paper_replication_sami.Rmd
after finish of draft

---
title: "Replication of \"Anti-Immigrant Rhetoric and ICE Reporting Interest: Evidence
  from a Large-Scale Study of Web Search Data\" paper"
author: "Ubaydul Sami"
date: "2024-06-24"
output: html_document
---

@@

          out = "table4_ols.html", # Save to HTML file
          type = "text", # You can also use "html" or "latex"
          intercept.bottom = FALSE,
          omit.stat = c("ser", "adj.rsq", "f", "aic"),
          notes = "Note: ∗p<0.1; ∗∗p<0.05; ∗∗∗p<0.01" )
```

>>>>

---
title: "Replication of \"Anti-Immigrant Rhetoric and ICE Reporting Interest: Evidence
  from a Large-Scale Study of Web Search Data\" paper"
author: "Ubaydul Sami and Buka Dikeocha"
date: "2024-06-24"
output:
  html_document: default
  pdf_document: default
---

@@

          out = "table4_ols.html", # Save to HTML file
          type = "text", # You can also use "html" or "latex"
          intercept.bottom = FALSE,
          omit.stat = c("ser", "adj.rsq", "f", "aic"),
          notes = "Note: ∗p<0.1; ∗∗p<0.05; ∗∗∗p<0.01" )
```
# Extension

## The paper shows increase in search of how to report of immigration violation but doesn't show if there were actual increase in number of reports / arrest/ deportation for immigration violation. For our research question we decided to find out if there was any increase of actual number of reports / arrest/ deportation for immigration violation.

**data source :** https://www.dhs.gov/ohss/topics/immigration/enforcement-and-legal-processes-monthly-tables

**link to data file:** https://onedrive.live.com/edit?id=6779012659AEA485%21120&resid=6779012659AEA485%21120&ithint=file%2Cxlsx&wdPreviousSession=2e2e85d3-ac39-43da-899d-f01ad6e066a7&wdo=2&cid=6779012659aea485

```{r}
google_term_data_report_extend <- 
  google_term_data_dummies |>
  filter(ymd >= '2014-01-01') |> 
  rename( year_month = ymd) |>
  select(year_month, year, month, president, immigr_report ) |>
  left_join(time_lines, by = "year_month") |>
  fill(time, .direction = c("down")) |> view()

head(google_term_data_report_extend)
```

```{r}
google_term_data_report_extend |>
  ggplot(aes(x = year_month, y = immigr_report, colour = time)) + 
  geom_point() + geom_smooth( se=FALSE) +
  geom_vline(data = time_lines, aes(xintercept = as.numeric(year_month)), linetype = "dotted", color = "black") +
  xlab("Year-month") +
  ylab("Immigration Reports search count") +
  ggtitle("Immigration report search")
```

ice <-
  read_csv("from_google_trends/ice_reportings.csv", skip = 4, col_names = c("year", "month", "reports", "reports_convicted", "", "", "", "reports_non_criminal", "", "")) %>%
  select(c(1, 2, 3, 4, 8)) %>%
  fill(year, .direction = "down") %>% 
  filter(month != "Total") %>%
  mutate(
    month = match(month, month.name),
    date = make_date(year, month)
  )

```{r}
ice_report_w_election <- 
  ice |>
  filter(date <= '2020-01-01') |> 
  rename( year_month = date) |>
  # select(year_month, year, month, president, immigr_report ) |>
  arrange(year_month) |>
  left_join(time_lines, by = "year_month") |>
  fill(time, .direction = c("down")) |>  view()

head(ice_report_w_election)
```

```{r}
ice_report_w_election %>%
  ggplot(aes(x = year_month, y = reports, colour = time)) + 
  geom_point() + geom_smooth( se=FALSE) +
  geom_vline(data = time_lines, aes(xintercept = as.numeric(year_month)), linetype = "dotted", color = "black") +

  xlab("Year-month") +

  ylab("Total Immigration Arrest") +

  ggtitle("Total Immigration Arrest by Year")

ice_report_w_election %>%
  ggplot(aes(x = year_month, y = reports_convicted, colour = time)) + 
  geom_point() + geom_smooth( se=FALSE) +
  geom_vline(data = time_lines, aes(xintercept = as.numeric(year_month)), linetype = "dotted", color = "black") +

  xlab("Year-month") +

  ylab("Convicted Immigration Arrest") +

  ggtitle("Convicted Immigration Arrest by Year")

ice_report_w_election %>%
  ggplot(aes(x = year_month, y = reports_non_criminal, colour = time)) + 
  geom_point() + geom_smooth( se=FALSE) +
  geom_vline(data = time_lines, aes(xintercept = as.numeric(year_month)), linetype = "dotted", color = "black") +

  xlab("Year-month") +

  ylab("Non-criminal Immigration Arrest") +

  ggtitle("Non-Criminal Immigration Arrest by Year")
